---
title: "`r params$title`"
author: "`r params$author`"
date: now
date-format: "MMMM D, YYYY"
format:
  html:
    theme:
      light: cosmo
      dark: darkly
    toc: true
    toc-location: left
    toc-title: "Table of Contents"
    number-sections: true
    embed-resources: true
    self-contained-math: true
execute:
  echo: false
  warning: false
  message: false
params:
  data_path: ""
  title: "NMA Preflight Diagnostics Report"
  author: "PreflightNMA"
---

```{r}
#| label: setup
library(preflightnma)
library(ggplot2)

# Load preflight data
preflight <- readRDS(params$data_path)
sparsity <- preflight$sparsity
```

<style>
.metrics-grid {
  display: grid;
  grid-template-columns: repeat(auto-fit, minmax(200px, 1fr));
  gap: 20px;
  margin-bottom: 30px;
  margin-top: 20px;
}

.metric-card {
  background: var(--bs-body-bg, #ffffff);
  border: 1px solid rgba(0,0,0,0.08);
  border-radius: 8px;
  padding: 20px;
  text-align: center;
  box-shadow: 0 4px 6px rgba(0, 0, 0, 0.02);
  transition: transform 0.2s, box-shadow 0.2s;
}

.metric-card:hover {
  transform: translateY(-2px);
  box-shadow: 0 6px 12px rgba(0, 0, 0, 0.05);
}

.metric-value {
  font-size: 2rem;
  font-weight: 700;
  color: var(--bs-primary, #0d6efd);
  margin-bottom: 5px;
}

.metric-label {
  font-size: 0.9rem;
  color: var(--bs-secondary, #6c757d);
  font-weight: 500;
  text-transform: uppercase;
  letter-spacing: 0.5px;
}

.metric-card.status-success .metric-value {
  color: #198754;
}

.metric-card.status-warning .metric-value {
  color: #fd7e14;
}

.report-section {
  margin-bottom: 40px;
}

.card-table-container {
  max-width: 500px;
  margin-top: 15px;
  margin-bottom: 25px;
}
</style>

## Executive Summary {.report-section}

Welcome to the Network Meta-Analysis (NMA) Preflight Diagnostics Report. This document provides automated checks to assess connectivity, transitivity (baseline covariate balance), sparsity, and potential covariate modifiers before fitting your NMA model.

## Network Sparsity {.report-section}

Network sparsity is the proportion of all possible pairwise treatment comparisons that do not have direct evidence from any clinical trial in your network.

<div class="metrics-grid">
  <div class="metric-card">
    <div class="metric-value">`r sparsity$n_treatments`</div>
    <div class="metric-label">Total Treatments</div>
  </div>
  <div class="metric-card">
    <div class="metric-value">`r sparsity$n_possible_comparisons`</div>
    <div class="metric-label">Possible Comparisons</div>
  </div>
  <div class="metric-card">
    <div class="metric-value">`r sparsity$n_observed_comparisons`</div>
    <div class="metric-label">Observed Comparisons</div>
  </div>
  <div class="metric-card status-`r if (sparsity$sparsity > 0.5) "warning" else "success"`">
    <div class="metric-value">`r sprintf("%.1f%%", sparsity$sparsity * 100)`</div>
    <div class="metric-label">Network Sparsity</div>
  </div>
</div>

```{r}
#| label: sparsity-message
#| results: asis
if (!is.null(sparsity$message)) {
  cat(paste0("> [!WARNING]\n> ", sparsity$message, "\n\n"))
}
```

### Observed Pairwise Comparisons

The table below lists all treatment pairs that are directly compared in at least one multi-arm study.

<div class="card-table-container">
```{r}
#| label: sparsity-table
if (!is.null(sparsity$observed_edges) && nrow(sparsity$observed_edges) > 0) {
  knitr::kable(
    sparsity$observed_edges,
    col.names = c("Treatment A", "Treatment B"),
    align = "cc",
    format = "html",
    table.attr = 'class="table table-hover table-striped"'
  )
} else {
  cat("No observed pairwise comparisons.\n")
}
```
</div>

## Network Connectivity {.report-section}

Connectivity plots illustrate the evidence structure. Nodes represent treatments (sized by total sample size across all arms), and edges represent direct evidence (thickness and transparency correspond to the number of studies comparing the connected treatments).

```{r}
#| label: connectivity-plots
#| results: asis
conn_plots <- preflight$connectivity_plots
if (length(conn_plots) == 0) {
  cat("No network connectivity plots were generated.\n")
} else {
  cat("::: {.panel-tabset}\n\n")
  for (plot_name in names(conn_plots)) {
    # Format the tab title cleanly
    tab_title <- gsub("_", " ", plot_name)
    tab_title <- paste0(toupper(substring(tab_title, 1, 1)), substring(tab_title, 2))
    
    cat(paste0("### ", tab_title, "\n\n"))
    print(conn_plots[[plot_name]])
    cat("\n\n")
  }
  cat(":::\n\n")
}
```

## Transitivity (Baseline Risk and Patient Characteristics) {.report-section}

Transitivity assumes that we can compare treatments indirectly via a common comparator. This requires data sources to be sufficiently similar in terms of baseline patient characteristics and other study designs. 

Below are the distributions of baseline patient characteristics across treatments to visually assess transitivity.

```{r}
#| label: transitivity-plots
#| results: asis
trans_plots <- preflight$transitivity_plots
if (length(trans_plots) == 0) {
  cat("No covariates were assessed or no transitivity balance plots were generated.\n")
} else {
  cat("::: {.panel-tabset}\n\n")
  for (cov_name in names(trans_plots)) {
    cat(paste0("### ", cov_name, "\n\n"))
    print(trans_plots[[cov_name]])
    cat("\n\n")
  }
  cat(":::\n\n")
}
```

## Covariate Modifier Assessments {.report-section}

Covariate modifiers can introduce inconsistency and heterogeneity if they are unbalanced across treatment comparisons. Here we present exploratory analyses for potential treatment effect modifiers.

```{r}
#| label: covariate-plots
#| results: asis
cov_plots <- preflight$covariate_plots
if (length(cov_plots) == 0) {
  cat("No covariate modifier plots were generated.\n")
} else {
  for (cov_name in names(cov_plots)) {
    cat(paste0("### Covariate: ", cov_name, "\n\n"))
    cat("::: {.panel-tabset}\n\n")
    
    plots_for_cov <- cov_plots[[cov_name]]
    
    if (!is.null(plots_for_cov$bubble_plot)) {
      cat("#### Meta-Regression (Bubble Plot)\n\n")
      print(plots_for_cov$bubble_plot)
      cat("\n\n")
    }
    
    if (!is.null(plots_for_cov$stratified_forest)) {
      cat("#### Stratified Forest Plot\n\n")
      print(plots_for_cov$stratified_forest)
      cat("\n\n")
    }
    
    if (!is.null(plots_for_cov$study_timeline)) {
      cat("#### Study Design Timeline\n\n")
      print(plots_for_cov$study_timeline)
      cat("\n\n")
    }
    
    cat(":::\n\n")
  }
}
```
